\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
Reply more comments.

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases overriding and
equational reasoning are both needed, especially when we use Coq to do
computation. For example, we may want a field to be an overridable 
monotonic function. We cannot split into two fields
\mintinline{Coq}{(f : nat → nat; p : monotonic f)}\YZ{Is this semicolon syntax valid Coq syntax?} because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---we allow the
users to specify the family/compiled module type\YZ{I don't understand "specify the family/compiled module type"}, and thus we can have a
\textit{locally transparent}, \textit{non-overridable} field located in
an \textit{overridable} family. Using the above example, we simply make
\mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an
\textit{overridable} family, but "f" to be non-overridable and
transparent on its definition, and thus we can prove "p". Once we want
to swap the implementation of "f", we just override the whole ``sealed''
family.

``Sealed'' families actually simulate interfaces in certain sense\YZ{I was actually thinking sealed families simulate sigma types, no?}---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.\YZ{I don't understand what it means to "assign each field with an axiom".}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

>>>>

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases overriding and
equational reasoning are both needed, especially when we use Coq to do
computation. For example, we may want a field to be an overridable 
monotonic function. We cannot split into two fields
\mintinline{Coq}{(f : nat → nat; p : monotonic f)}\YZ{Is this semicolon syntax valid Coq syntax?}\EDJreply{No, this part is just pseudo-code for two consecutive fields. I have no good idea on what to use other than semicolon, apparently I cannot use comma.} because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---we allow the
users to specify the compiled module type of a given family\YZ{I don't understand "specify the family/compiled module type"}\EDJreply{Sorry. I rephase it into "compiled module type of a given family".}, and thus we can have a
\textit{locally transparent}, \textit{non-overridable} field located in
an \textit{overridable} family. Using the above example, we simply make
\mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an
\textit{overridable} family, but "f" to be non-overridable and
transparent on its definition, and thus we can prove "p". Once we want
to swap the implementation of "f", we just override the whole ``sealed''
family.

``Sealed'' families can actually simulate interfaces in certain sense\YZ{I was actually thinking sealed families simulate sigma types, no?}\EDJreply{You are absolutely right. I should add a "can" here. I can use sealed family to simulate interface is by creating a sigma type, but making the impleemntation of sigma type trivial (using place holder/using axiom as I specified below). Then once I want to instantiate with real implementation, I override the whole family -- as long as it has the same type as the sealed family, everything still works.}---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.\YZ{I don't understand what it means to "assign each field with an axiom".}\EDJreply{It really means ``place holder'' in general programming language (Python's NonImplement()), defer to future. Because Coq's Axiom can be used to instantiate anything.}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property
